### 2014-04-16 doc/uist14/iteration3.tex
Updates to iteration 3 using Ben's feedback
* Shorten the overall section
* Removed unnecessary details from technical section
* Separated user facing from technical facing

In our third iteration, we ask the question ``can we build a system which further minimize the chance of falling back to list based refinement?''

\subsection{Technique}
The motion sensors (including gyroscope, magnetometer and accelerometer) on the head-worn device can help us determine the orientation of a user's head. However, this absolute orientation cannot be directly used in any indoor environment as the user may change their location. However, as long as the targets are spread around the periphery, their relative orientation to each other is relatively stable (see Figure~\ref{fig:third_principle}). This key observation inspires us to investigate a hybrid solution with IR and orientation sensors on Glass.

@@

In the first stage, the user orients their head towards each device, and the system learns a map of the devices based on their corresponding sensor readings. During the second stage, when the user wishes to use head-motion for disambiguation, they will put their finger on the touchpad to enter a quasi-mode in which their head movement is used to select targets. In this mode, only one device has a solid indicator light on at a time. \bjoern{revisit prior sentence - there's a problem in the current technique in that the user doesn't know which targets are in the refinement set and which aren't.} \achal{There is no longer a refinement set - instead the user can select between all the devices using just orientation once they enter quasi mode.} The user can then tilt in the direction of the device they wish to switch to. This gesture is inspired by observing users who tend to adjust their glasses for closer inspection.

The technical implementation of this interaction involves a number of subtleties due to the noisiness of our data. Absolute orientations between devices change frequently at the slightest user movement, and motion sensor data is inherently noisy. To alleviate the second issue, a low-pass filter is applied to the measurements, allowing us to extract the direction of motion from this smoothed history. Empirically, we found that we can reliably detect the direction of movement with 100ms of history and a sensor resolution of 10ms.

Orientation changes can be overcome by using a hybrid of absolute and relative orientations augmented by IR information. While absolute orientations are unstable, relative orientations do not contain information for essential tasks, such as adding devices to a learned map. Our system stores the absolute orientations of each device during the learning stage, but utilizes only the relative information embedded in this data for disambiguation. Once the user is in quasi-mode, our system calculates the user's direction of motion as described earlier, and searches through the map for the nearest device in that direction. Thus, although the absolute orientation of the currently lit device may be incorrect, the relative information can still be used for disambiguation. Finally, the system uses hysteresis to prevent the user from accidentally jumping repeatedly between devices by switching devices only once the user has moved beyond a certain threshold in any direction. \achal{I understand hysteresis, but I can't figure out how the word can be used naturally (as there's no way to say a system "has" hysteresis). This last sentence may require rewording.}

\bjoern{how well will this work if the user shifts position within a room?}
\achal{I think the updates should explain this now.}

\achal{Not sure if there should be a conclusion of some sort here.}

>>>>

\achal{This used to have an explicit question which I removed, as it sounded
very unnatural.}
In our third iteration, we build a system which further minimizes the chance of
falling back to list based refinement.

\subsection{Technique}
The motion sensors (including gyroscope, magnetometer and accelerometer) on the
head-worn device can help us determine the orientation of a user's head.
Unfortunately, this absolute orientation cannot be directly used in any indoor
environment as the user may change their location. As long as the targets are
spread around the periphery, however, their relative orientations are stable
(see Figure~\ref{fig:third_principle}). This key observation inspires us to
investigate a hybrid solution with IR and orientation sensors on Glass.

@@

In the first stage, the user orients their head towards each device, and the
system learns a map of the devices based on their corresponding sensor readings.
During the second stage, when the user wishes to use head-motion for
disambiguation, they will put their finger on the touchpad to enter a
quasi-mode, where only one device has a solid indicator light on at a time. This
gesture is inspired by observing users who tend to adjust their glasses for
closer inspection. The user can then tilt in the direction of the device they
wish to switch to. The system then uses its understanding of the relative
locations of the devices to create an {\em adjacency map}.

The technical implementation of this interaction involves a number of subtleties
due to the noisiness of our data. As mentioned earlier, absolute orientations
of devices change frequently at the slightest user movement. Unfortunately,
while relative orientation information is more stable, it does not contain
the necessary information for essential tasks, such as adding devices to a
learned map. To overcome these issues, we implement a hybrid method using
absolute and relative orientations augmented by IR information. Our system
stores the absolute orientations of each device during the learning stage, but
utilizes only the relative information for disambiguation. Once the user is in
quasi-mode, our system calculates the user's direction of motion using a
low-passed history of sensor measurements, and searches through the devices for
the nearest device in that direction. Thus, although the absolute orientations
may be incorrect, the relative information can still be used for disambiguation.
